### 2020-08-25 manuscript/PLOS-MSc-Thesis.tex
extend abstract results section

\subsection*{Results}
Out of 2061 GRNs selected using the genetic algorithm, 714 groups of 
topologies were found that were able to interpret a morphogen input. The 
main network motif involved in the formation of the band expression pattern 
was the type 3 Incoherent Feed Forward Loop (I3-FFL); we also present here 
other network topologies that have not been previously reported.

>>>>

\subsection*{Results}
Out of 2061 GRNs selected using the genetic algorithm, 714 groups of 
topologies were found that were able to interpret a morphogen input. The 
main network motif involved in the formation of the band expression pattern 
was the type 3 Incoherent Feed Forward Loop (I3-FFL); we also present here 
other network topologies that have not been previously reported and that can 
be useful as synthetic regulatory networks due to its relatively simple design 
and robust morphogen interpretation mechanisms.
